Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
merging

\brian{Symplectic, non-polarized version needed for 6d N=(1,0).}

@@

\begin{landscape}
\begin{figure}
\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
\node (825) [right=of 82] {};
\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};

\node (2d) [dimension, left=of 21] {2d};
\node (3d) [dimension, above=of 2d] {3d};
\node (4d) [dimension, above=of 3d] {4d};
\node (5d) [dimension, above=of 4d] {5d};
\node (6d) [dimension, above=of 5d] {6d};
\node (7d) [dimension, above=of 6d] {7d};
\node (8d) [dimension, above=of 7d] {8d};
\node (9d) [dimension, above=of 8d] {9d};
\node (10d) [dimension, above=of 9d] {10d};
\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}
\end{landscape}

>>>>

\brian{Symplectic, non-polarized version needed for 6d N=(1,0).} \chris{following Brian's suggestion I've used the term: holomorphic BF theory coupled to a higher holomorphic symplectic boson, valued in a representation $U$.  If we continue to use that term, we should explain it here.}

@@

%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE

% \begin{landscape}
% \begin{figure}
% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
% \node (825) [right=of 82] {};
% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
% 
% \draw[arrow] (101) -- (91);
% \draw[arrow] (91) -- (81);
% \draw[arrow] (91) -- (82);
% \draw[arrow] (81) -- (71);
% \draw[arrow] (82) -- (71);
% \draw[arrow] (82) -- (72);
% \draw[arrow] (83) -- (73);
% \draw[arrow] (71) -- (61);
% \draw[arrow] (71) -- (62);
% \draw[arrow] (72) -- (62);
% \draw[arrow] (72) -- (63);
% \draw[arrow] (73) -- (65);
% \draw[arrow] (61) -- (51);
% \draw[arrow] (62) -- (51);
% \draw[arrow] (62) -- (52);
% \draw[arrow] (63) -- (53);
% \draw[arrow] (64) -- (52);
% \draw[arrow] (64) -- (54);
% \draw[arrow] (65) -- (54);
% \draw[arrow] (51) -- (41);
% \draw[arrow] (51) -- (42);
% \draw[arrow] (52) -- (42);
% \draw[arrow] (52) -- (43);
% \draw[arrow] (53) -- (43);
% \draw[arrow] (54) -- (43);
% \draw[arrow] (54) -- (44);
% \draw[arrow] (54) -- (45);
% \draw[arrow] (41) -- (31);
% \draw[arrow] (42) -- (31);
% \draw[arrow] (42) -- (32);
% \draw[arrow] (43) -- (32);
% \draw[arrow] (44) -- (32);
% \draw[arrow] (45) -- (32);
% \draw[arrow] (31) -- (21);
% \draw[arrow] (31) -- (22);
% \draw[arrow] (32) -- (22);
% 
% \node (2d) [dimension, left=of 21] {2d};
% \node (3d) [dimension, above=of 2d] {3d};
% \node (4d) [dimension, above=of 3d] {4d};
% \node (5d) [dimension, above=of 4d] {5d};
% \node (6d) [dimension, above=of 5d] {6d};
% \node (7d) [dimension, above=of 6d] {7d};
% \node (8d) [dimension, above=of 7d] {8d};
% \node (9d) [dimension, above=of 8d] {9d};
% \node (10d) [dimension, above=of 9d] {10d};
% \end{tikzpicture}
% \caption{Orbits of square-zero supercharges.}
% \label{fig:superchargeorbits}
% \end{figure}
% \end{landscape}
